<div>Runye Hu A13410385</div>
<div>Yijie Fan A13485989</div>
<div>Xinyi He A13561164</div>
<div>Yifan Wu A14060535</div>
<div>Yiwen Cai A13530685</div>


---
title: "HW2"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Problem1
###Nutrient data
```{r}
nutrient=read.table("https://www.math.ucsd.edu/~wez243/data/nutrient.txt")
nutrient$V1=NULL
colnames(nutrient)=c("Calcium", "Iron", "Protein", "Vitamin A", "Vitamin C")
```

###Q1:
```{r}
means <- colMeans(nutrient, na.rm = TRUE)
print(means)
sd <- apply(nutrient, 2, function(x) sd(x, na.rm = TRUE))
print(sd)
```

###Q2:
```{r}
intake = c(1000,15,60,800,75)
p_val = c();
for (i in 1:ncol(nutrient)){
  p = t.test(nutrient[i],alternative = c("two.sided"),mu = intake[i], paired = FALSE,conf.level = 0.95)$p.value
  p_val = c(p_val,p)
}
p_val
ans = p_val > matrix(0.05,1,ncol(nutrient))
ans
```

###Q3:
<div>For Calcium, Iron, Protein we reject the hypotheses that the population mean of that variable equals the recommended values because their p-value are less than significance level.</div> 
<div>For VitaminA and VitaminC, we don't have enough evidence to reject because their p-value are larger than significance level. Therefore, we conclude that the US women don't meet the recommended nutrient intake amount. </div>
<div>My recommendation is that US women should intake more food with rich Calcium and Iron while intaking a little bit less protein.</div>


###Problem2
###Multiple data
```{r}
multiple = read.table("~/Downloads/multiple.txt");
```

###Q1:
```{r}
p_val = c()
ans = c()
for (i in 1:50){
  p = t.test(multiple[i], alternative = c("two.sided"),mu = 0,paired = FALSE,conf.level = 0.9)$p.value
  p_val = c(p_val,p)
}
p_val
ans = p_val > matrix(0.1,1,50)
ans
```
So the population mean vector doesn't equal to a vector whose elements are all zeros.

###Q2:
```{r}
type1 = 4
type1
type2 = 0
type2
FWER = 1-(1-0.1)^50
FWER
FDP = type1/(50-sum(ans))
FDP
```
<div>Number of Type 1 Error: 4</div>
<div>Number of Type 2 Error: 0</div>
<div>FWER: 0.9948462</div>
<div>FDP: 0.2857143</div>

###Q3:
```{r}
p_B = c()
ans_B = c()
for (i in 1:50){
  p = t.test(multiple[i], alternative = c("two.sided"),mu = 0,paired = FALSE,conf.level = 0.9)$p.value
  p_B = c(p_B,p)
}
p_B
ans_B = p_B > matrix(0.1/50,1,50)
ans_B
FWER = 1-(1-0.1/50)^50
FWER
power = 10/10
power
```
<div>FWER:0.09525318</div>
<div>power:1 </div>

###Q4:
```{r}
p_value = c()
ans_BH = c()
for (i in 1:50){
  p = t.test(multiple[i], alternative = c("two.sided"),mu = 0,paired = FALSE,conf.level = 0.9)$"p.value"
  p_value = c(p_value,p)
}

bh <- function(p,alpha)
{
  m <- length(p)
  l <- alpha*c(1:m)/m
  result <- matrix(TRUE,1,m)
  sort_p <- sort(p) 
  set <- which(l>=sort_p)
  if(length(set)==0){
    rej <- set
  } else{
    imax <- max(set)
    threshold <- sort_p[imax]
    rej <- which(p <= threshold)
  }
  result[rej] = FALSE;
  
  outlist<-list(result = result)
  return(outlist)
}

bh_test <- bh(p_value,0.1)
p_value
ans_BH = bh_test$result
ans_BH
```

```{r}
FDP = 0/sum(ans_BH)
FDP
power = 10/10
power
```
<div>FDP: 0 </div>
<div>power:1 </div>
<div>By using BH method, we improve from the result of naive multiple testing and multiple testing with Bonferroni method.</div>
<div>In 2.1(naive multiple testing part), we have 4 Type I error, while we make no Type I error using BH method. </div>
<div>For 2.3 and 2.4, type I and type II errors are the same(we make no errors), and thus they both work good for this case.</div>
